A geographic routing approach for IPv6 in low-powered and lossy large-scale wireless networks

### 2015-03-30 2014_ELSEVIER_CEE_SI/paper_cee_special_issue.tex
adição de biografia

>>>>

\noindent {\bf Gustavo Weber Denardin}
received his B.Eng., M.Eng. and Ph.D. degrees in Electrical Engineering from Federal University of Santa Maria, Brazil, in 2002, 2004 and 2012, respectively. He joined the Department of Electronics at Federal University of Technology - Parana (UTFPR) in 2005, where he is currently an associate professor. His research interests include embedded systems, Real-time Operating Systems, wireless sensor/actuator networks and its applications in lighting and power systems.\newline
